---
title: "AN_markdown_ReProDat_pr1"
author: "AN"
date: "5/27/2020"
output: html_document
---
# Download file from web
### urlarch = "https://www.coursera.org/learn/reproducible-research/peer/gYyPt/course-project-1.zip"
### A.Loading and preprocessing the data
### unzip data and read 
### csvFile = unz(temp, "activity.csv")
```{r} 
activityFile <- "~/Desktop/Coursera_2020/Reproducible_research/week2project/activity.csv"
steps_data <- read.csv(activityFile, header = TRUE) 
head(steps_data)
```
# 1. Calculate total number of steps taken each day
## 1.1. Calculate the total number of steps taken per day
```{r} 
library(magrittr)
library(dplyr)
data_by_date <- steps_data %>% select(date, steps) %>% group_by(date) %>% summarize(tsteps= sum(steps)) %>%na.omit()
data_by_date
```
## 1.2. Calculate and report the mean and median of the total number of steps taken per day
```{r}
mean(data_by_date$tsteps)
median(data_by_date$tsteps)
```
## 1.3. Plot a histogram of the total number of steps taken each day 
```{r}
hist(data_by_date$tsteps, xlab = "Total daily Steps",main="Histogram of Total Steps by day", 
     breaks = 20)
```

# 2.The average daily activity plot for every 5 mins interval and contains the maximum number of steps

```{r}
library(ggplot2)
data_by_interval <- steps_data%>% select(interval, steps) %>% na.omit() %>% group_by(interval) %>% summarize(tsteps= mean(steps)) 
ggplot(data_by_interval, aes(x=interval, y=tsteps))+ geom_line()
data_by_interval[which(data_by_interval$tsteps== max(data_by_interval$tsteps)),]
```
# 3.Imputing missing values
## Total number of missing values in the dataset
```{r}
missing_Vals <- sum(is.na(data))
missing_Vals
```

## 3.1.Strategy for filling in all of the missing values in the dataset
```{r}
library(magrittr)
library(dplyr)
replace_with_mean <- function(x) replace(x, is.na(x), mean(x, na.rm = TRUE))
meandata <- steps_data%>% group_by(interval) %>% mutate(steps= replace_with_mean(steps))
head(meandata)
```
## 3.2.A new dataset that is equal to the original dataset but with the missing data filled 
```{r}
FullSum_DataBy_Day <- aggregate(meandata$steps, by=list(meandata$date), sum)
names(FullSum_DataBy_Day)[1] ="date"
names(FullSum_DataBy_Day)[2] ="totalsteps"
head(FullSum_DataBy_Day,15)
```
## 3.3.A histogram of the total number of steps taken per day. 
```{r}
hist(FullSum_DataBy_Day$totalsteps, xlab = "Steps",
     ylab = "Frequency", main = "Total Daily Steps", breaks = 20)
```
## 3.4.Compare the mean and median of Old and New data
```{r}
oldmean <- mean(data_by_date$tsteps, na.rm = TRUE)
newmean <- mean(FullSum_DataBy_Day$totalsteps)
```
## 3.5.Old mean and New mean
```{r}
oldmean
newmean
```
## 3.6.Old median and New median
```{r}
oldmedian <- median(data_by_date$tsteps, na.rm = TRUE)
newmedian <- median(FullSum_DataBy_Day$totalsteps)
```
```{r}
oldmedian
newmedian
```
# 4. Are there differences in activity patterns between weekdays and weekends?
```{r}
meandata$date <- as.Date(meandata$date)
meandata$weekday <- weekdays(meandata$date)
meandata$weekend <- ifelse(meandata$weekday=="Saturday" | meandata$weekday=="Sunday", "Weekend", "Weekday" )
library(ggplot2)
meandataweekendweekday <- aggregate(meandata$steps , by= list(meandata$weekend, meandata$interval), na.omit(mean))
names(meandataweekendweekday) <- c("weekend", "interval", "steps")
ggplot(meandataweekendweekday, aes(x=interval, y=steps, color=weekend)) + geom_line()+
  facet_grid(weekend ~.) + xlab("Interval") + ylab("Mean of Steps") +
  ggtitle("Comparison of Average Number of Steps in Each Interval")
```
